### 2017-10-23 paper.tex

One popular lesson development methodology is presented in \cite{wiggins-mctighe}.
When this is used,
lessons are built by:

  \item
    identifying learning objectives,

  \item
    creating \emph{summative assessments} to determine whether those objectives have been met,

  \item
    designing \emph{formative assessments} to gauge learners' progress
    and give them a chance to practice key skills,

  \item
    putting those formative assessments in order,

  \item
    and only then writing lessons to connect each to the next.

\noindent
This method is effective in its own right,
but its greatest benefit is that it gives everyone a framework for collaboration.

An example of how to teach these practices is Software Carpentry's (\url{https://software-carpentry.org/}) instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
This program teaches good pedagogical practices,
and introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.

>>>>

By way of example, Software Carpentry encourages its volunteers to use
the popular lesson development methodology presented by \cite{wiggins-mctighe},
whereby learning objectives and assessments are created \emph{before} any lesson materials are developed.
In particular, \emph{summative assessments} are created to determine whether the learning objectives have been met,
and \emph{formative assessments} are created to gauge learners' progress and to give them a chance to practice key skills.
The completed formative assessments are put in order and only then are the lessons written, 
with the aim of connecting each formative assessment to the next.
This method is effective in its own right,
but its greatest benefit is that it gives everyone a framework for collaboration.

An example of how to teach such pedagogical practices
is Software Carpentry's (\url{https://software-carpentry.org/}) instructor training program.
First offered in 2012,
it is now a two-day course delivered both in-person and online
\cite{lessons-learned,instructor-training,how-to-teach-programming}.
In addition to a focus on pedagogy,
the course introduces everyone who takes it to who Software Carpentry's lessons are for,
how they are delivered,
and how they are maintained.
Largely as a result of this training,
several hundred people per year now contribute to Software Carpentry's lessons.
